Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-02-23 First_np_Paper/first_np_paper.tex
Updated a few XS figures, added 2 comments to manuscript
Added new decay curve figure for 336keV, to test direct labeling of figures
Updated abstract and front matter with Lee edits

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research A}

@@

%% Give the abbreviation of the Journal.
\jid{nima}
% \jid{yspmi}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Nucl Instrum Meth A}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
\title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies}

% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

\comment{Use D-D or DD as convention?}

\comment{Choose a preferred title...}

% \comment{Need Daniel's middle initial}

\comment{Should street address be included for each institution, or just city / state / zip?}

Neutron activation cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production reactions have been measured for quasi-monoenergetic 2.7645 MeV incident neutrons produced by the UC Berkeley High Flux Neutron Generator, a D-D plasma-based neutron source. \comment{ Need to decide on number of sig figs to report, and truncate appropriately - i.e.2.76 +0.15 - 0.22 - \#s taken from text section 3]
} Measurements were performed using activation ratio methods, measured relative to co-irradiated indium foils using the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions. The use of thin foils and gamma spectroscopy using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty. These cross section measurements show good agreement with the literature and theoretical values, but with lower uncertainty than existing measurements. This work has resulted in a detailed characterization of the D-D plasma-based neutron source, which can be used for other low-energy neutron reaction cross section measurements in the future.

\comment{Abstract needs fleshing out.}

@@

A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes, as many of these cross sections currently have not been measured, or possess significant uncertainties.   One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from D-D neutron generators. Direct neutron activation, using a D-D neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production. Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective. Notably, the higher penetration of neutrons allows for the use of thick target designs, which can improve production throughput and greatly simplifies target cooling considerations. More importantly, low-energy neutron reactions can be used to prevent competing reaction channels in a charged-particle reaction which would otherwise contaminate the product specific activity.

@@

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a D-D neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for D-D fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}. Within the center of the target (at 8 mm from the D-D reaction surface), samples may be inserted prior to  HFNG startup. \autoref{fig:hfng_b} displays the target setup. At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.

@@

Direct activation of a thin foil can be used for high-fidelity measurement of neutron-induced reactions, through subsequent decay spectroscopy. This method can provide cross sections with far lower uncertainty than neutron time-of-flight measurements, but is heavily reliant upon precisely quantifying the neutron fluence incident upon a loaded target. To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions. In addition, over the energy region spanned by the D-D emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements. The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.

@@

The kinematics of D-D fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam. This distribution is a function of the incident deuteron kinetic energy, and has been well-documented \cite{Liskien_Paulsen_1973}; \autoref{fig:scatt_angle} displays the energy-angle distribution for the incident 100 keV deuterons used in the HFNG.

@@

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
 % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
 \caption{Energy-angle distribution for neutrons emitted following D-D fusion, for 100 keV incident deuterons.}
 \label{fig:scatt_angle}
\end{figure}

Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target. Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the D-D reaction surface. This would greatly reduce the flux (to approximately 10$^4$ neutrons/s\ cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production and decay in activation measurements. Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the D-D reaction surface. This allows the samples to subtend a fairly narrow ($\sim$28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately $\sci{1.3}{7}$neutrons/s\ cm$^2$ ) flux for activations.

@@

To determine the energy distribution of neutrons incident upon the loaded foils following production and transport, the Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}). This spectrum illustrates the forward-focused kinematics of the D-D reaction subtended by the co-loaded sample foils.

@@

While this shows that the sample foils receive a very narrow energy distribution of incident neutrons, an effective neutron energy and energy bounds must be determined to constrain cross section ratio measurements. From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils. Due to the kinematics of D-D neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV. For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:

@@

This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}. Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions. Within 1 standard deviation above and below the centroid, 68.2\% of all reactions should be encompassed. Thus, the upper and lower energy uncertainties correspond to the neutron energies $E'$  such that $F\pp{E'}$ = 0.841 and $F\pp{E'}$ = 0.159, respectively. From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.  This 37-keV full-energy spread verifies that, at such close distances to the D-D reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.

@@

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[width=5in]{./figures/ti_foils.png}
        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
        \label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
                \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production.}
     \label{fig:main_spectra}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/336keV_curve2.png}
        \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
        \label{fig:decay_curve_336}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
        \label{fig:decay_curve_391}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[scale=0.6]{./figures/417keV_curve2.png}
        \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
                \label{fig:decay_curve_417}
    \end{subfigure}
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/511keV_curve2.png}
        \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
        \label{fig:decay_curve_511}
    \end{subfigure}%
    \caption{Decay curves used to verify photopeak transition assignment.}
     \label{fig:decay_curves}
\end{figure*}

@@

\comment{Add in EMPIRE data points?}

@@

Using direct activation methods for thin foils as described in this work, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections have been measured for  2.7645 MeV neutrons, to within 6\% uncertainty. These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements. The use of D-D neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies. While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the D-D neutron emission energy spectrum.

>>>>

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research B}

@@

%% Give the abbreviation of the Journal.
\jid{nimb}
% \jid{yspmi}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Nucl Instrum Meth B}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
\title{Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies}

% \title{(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via DD Neutron Generator\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

@@

%\comment{Use DD or DD as convention?}

% \comment{Need Daniel's middle initial} - he doesn't have one

Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator. The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes. The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples. Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 6\% uncertainty. The cross section were determined with lower uncertainty than existing measurements and are found to be  in good agreement with the literature and theoretical values. This work highlights the utility of using D-D plasma-based neutron sources, for a host of nuclear data measurements and potentially for the production of radionuclides for medical applications.

\comment{The abstract is now nicely short and sweet, but should it be expanded at all?}

@@

A series of experiments are being conducted at UC Berkeley to measure low-energy neutron-induced production cross sections for a range of emerging medical radioisotopes, as many of these cross sections currently have not been measured, or possess significant uncertainties.   One potential method for producing many of these isotopes is the use of (n,p) reactions via neutron beams from DD neutron generators. Direct neutron activation, using a DD neutron generator, allows for more precise cross section measurements than time-of-flight methods, and potentially offers a proliferation-resistant pathway for radioisotope production. Neutron activation can provide several advantages over charged-particle reactions from a targetry perspective. Notably, the higher penetration of neutrons allows for the use of thick target designs, which can improve production throughput and greatly simplifies target cooling considerations. More importantly, low-energy neutron reactions can be used to prevent competing reaction channels in a charged-particle reaction which would otherwise contaminate the product specific activity.

@@

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley, seen in  \autoref{fig:hfng_a}. This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam 5 mm in diameter. This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of lab emission angle \cite{Liskien_Paulsen_1973}. Within the center of the target (at 8 mm from the DD reaction surface), samples may be inserted prior to  HFNG startup. \autoref{fig:hfng_b} displays the target setup. At the time of the presented experiments, the machine operated under nominal conditions of a 100 kV deuterium beam extracted at 1.5 mA, creating a fluence of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$ on the target.

@@

Direct activation of a thin foil can be used for high-fidelity measurement of neutron-induced reactions, through subsequent decay spectroscopy. This method can provide cross sections with far lower uncertainty than neutron time-of-flight measurements, but is heavily reliant upon precisely quantifying the neutron fluence incident upon a loaded target. To avoid the introduction of this large uncertainty, 0.5-mm thin Indium foils were co-loaded along with each target foil for irradiation, with all production cross sections thus measured relative to the well-characterized \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} dosimetry standard reactions. In addition, over the energy region spanned by the DD emission spectrum, the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} reaction cross sections are nearly constant, which greatly simplifies the (Zn/In) and (Ti/In) ratio measurements. The use of this well-established ratio method removes the fluence dependence from all cross-section calculations, removing the largest source of systematic uncertainty in activation.

@@

The kinematics of DD fusion at 100 keV lab energy produce neutrons of energy ranging from 2.2 to 2.85 MeV, over the lab-frame emission angular range of 0-180\degree, with respect to the incident deuteron beam. This distribution is a function of the incident deuteron kinetic energy, and has been well-documented \cite{Liskien_Paulsen_1973}; \autoref{fig:scatt_angle} displays the energy-angle distribution for the incident 100 keV deuterons used in the HFNG.

@@

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{./figures/scatt_angle.pdf}
 % scatt_angle.pdf: 369x295 pixel, 72dpi, 13.02x10.41 cm, bb=0 0 369 295
 \caption{Energy-angle distribution for neutrons emitted following DD fusion, for 100 keV incident deuterons.}
 \label{fig:scatt_angle}
\end{figure}

Collimated beamlines can be used to select an energy group from this distribution, by permitting only neutrons within a certain angular window to be incident upon a target. Due to the compact nature of the HFNG, this would require the mounting of samples outside of the target chamber, with a distance of at least 20 cm from the DD reaction surface. This would greatly reduce the flux (to approximately 10$^4$ neutrons/s\ cm$^2$ over 4$\pi$) subtended by a single target and require longer irradiations for activation, which exacerbates the effect of simultaneous production and decay in activation measurements. Instead, the samples are mounted internally in the HFNG target chamber, separated by 5 mm of copper from the DD reaction surface. This allows the samples to subtend a fairly narrow ($\sim$28\degree) angle of the forward-focused neutrons, while maintaining the high (approximately $\sci{1.3}{7}$neutrons/s\ cm$^2$ ) flux for activations.

@@

To determine the energy distribution of neutrons incident upon the loaded foils following production and transport, the Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}). This spectrum illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.

@@

While this shows that the sample foils receive a very narrow energy distribution of incident neutrons, an effective neutron energy and energy bounds must be determined to constrain cross section ratio measurements. From the same MCNP6 simulation, flux tallies show a flux-weighted average neutron energy of 2.7645 MeV in the Indium foil, and 2.7649 MeV in the zinc or titanium foil; these are indistinguishable within statistical uncertainty, and serve as an effective neutron energy in the loaded target foils. Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.7825 MeV. For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is simply:

@@

This quantity $F\pp{E'}$ is plotted in \autoref{fig:frac_plot}. Using the flux-averaged neutron energy in the Indium foil as a centroid, this fraction of total reactions can be used to estimate the uncertainty in effective neutron energy, which will become energy error bars in the excitation function for these reactions. Within 1 standard deviation above and below the centroid, 68.2\% of all reactions should be encompassed. Thus, the upper and lower energy uncertainties correspond to the neutron energies $E'$  such that $F\pp{E'}$ = 0.841 and $F\pp{E'}$ = 0.159, respectively. From \autoref{eqn:react_fraction},  these are found to be  F(2.7796 MeV) = 0.841 and F(2.7426 MeV) = 0.159, respectively; thus the effective neutron energy subtended by target foils is reported as $E_n$ = 2.7645 MeV + 0.0151 MeV / - 0.0219 MeV.  This 37-keV full-energy spread verifies that, at such close distances to the DD reaction surface, loaded target foils receive a highly quasi-monoenergetic neutron flux.

@@

\begin{figure*}[H]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[width=5in]{./figures/ti_foils.png}
        \includegraphics[width=5in]{./figures/47sc_gspectrum_alt.pdf}
        \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a planar LEPS detector}
        \label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \includegraphics[width=5in]{./figures/64Cu_gspectrum_alt.pdf}
        \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
                \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production.}
     \label{fig:main_spectra}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/336keV_curve_new.pdf}
        \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
        \label{fig:decay_curve_336}
    \end{subfigure}%
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \includegraphics[scale=0.6]{./figures/391keV_curve_new.pdf}
        \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
        \label{fig:decay_curve_391}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
        \includegraphics[scale=0.6]{./figures/417keV_curve2.png}
        \caption{Decay curve for the $\beta^-$ decay of \ce{^{116}In}.}
                \label{fig:decay_curve_417}
    \end{subfigure}
     \begin{subfigure}[t]{0.49\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[scale=0.6]{./figures/511keV_curve2.png}
        \caption{ Decay curve for the $\beta^+$ decay of \ce{^{64}Cu}.}
        \label{fig:decay_curve_511}
    \end{subfigure}%
    \caption{Decay curves used to verify photopeak transition assignment.}
     \label{fig:decay_curves}
\end{figure*}

@@

\comment{Waiting on Lee for EMPIRE, ALICE data and language discussing differences and the significance of this.}

@@

Using direct activation methods for thin foils as described in this work, the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production cross sections have been measured for  2.7645 MeV neutrons, to within 6\% uncertainty. These measurements are consistent with experimental data and theoretical models,  and have been measured to lower uncertainty than existing measurements. The use of DD neutron generators can be an efficient pathway for the measurement of these low-energy (n,p) reaction channels, as well as a relative method used to normalize measurements at higher neutron energies. While it reduces the neutron flux incident upon target foils, the use of collimated beam lines to irradiate foils at various angles allows a single neutron generator to perform these measurements at various other energies throughout the DD neutron emission energy spectrum.
